Efectividad de reservas marinas en México

### 2018-01-11 Manuscript.Rmd
Added latex template for manuscript skeleton

---
title: "Efectividad de reservas marinas en México"
author: "Juan Carlos Villaseñor-Derbez, Stuart Fulton, Jorge Torre"
header-includes:
- \usepackage{setspace}
- \doublespacing
- \renewcommand{\contentsname}{Contenidos}
output:
  pdf_document:
    fig_caption: yes
    toc: yes
fontsize: 12pt
bibliography:
- exported-references.bib
csl: huct.csl
---

>>>>

---
title: "Efectividad de reservas marinas en México"
author: "Juan Carlos Villaseñor-Derbez, Stuart Fulton, Alvin Suárez-Castillo"
header-includes:
- \usepackage{setspace}
- \doublespacing
- \renewcommand{\contentsname}{Contenidos}
output:
  pdf_document:
    fig_caption: yes
    toc: yes
fontsize: 12pt
bibliography:
- exported-references.bib
csl: huct.csl
---
